---
title: "FRRO2Compare2"
author:
- Douglas A. Campbell
- Maximilian Berthold
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
Compare [O2] to FRRf data for a dataset.

Define time windows defined by changes in PAR imposed by script from FRRf changes in PAR.
For each run create a series of nests of [O2] data from optode for each PAR level and each TempCont setting.
Trim [O2] data nests to remove first 60 rows (~ 60 s) of 180 rows (~ 180 s) to avoid initial induction period.
Fit slopes of umol O2  l~-1~ s~-1~ for each PAR level nest.
Generate estimates of gross umol O2  l~-1~ s~-1~ by subtracting dark respiration rates.
  Initial and final O2 respiration rate estimators; average? chose?
  
Plot gross umol O2  l~-1~ s~-1~ vs. PAR to detect outliers.

i. Compare O2 l~-1~ s~-1~ slopes for each PAR to estimates of PSII ETR e- PSII~-1~ s~-1~ taken from FRR measures at that same PAR level.
  This calibration gives us an estimate of [PSII] because:
  O2 l~-1~ s~-1~ = (e- PSII~-1~ s~-1~)/4 * [PSII], so
  [PSII] = O2 l~-1~ s~-1~ * 4/(e- PSII~-1~ s~-1~)

For a given sample [PSII] should be a constant; any change in O2 l~-1~ s~-1~ with increasing PAR or changing actinic light colour should be driven solely by changes in e- PSII~-1~ s~-1~.  If apparent [PSII] changes this indicates issues with measurements, as for example recycling of electrons leaving PSII back to reduction of O2 induced under high light, which lowers measured O2 l~-1~ s~-1~, or distortions under different excitation colours 450 nm vs. 590 nm.

ii.  Comparing results from different samples and light levels and light qualities, generate calibration(s) for fluorescence based estimators of [PSII] like Fo/sigmaPSII.
  
iii. Compare O2 l~-1~ s~-1~  slopes for each PAR to estimates of JVPSII e- L~-1~ s~-1~ taken from FRR measures.
  This direct calibration gives us a fluorescence based calibrated estimate of e- L~-1~ s~-1~, for later comparison with growth rates, cell counts, etc.

# Set General Variable Values
## Run specific variables start at Line 122

## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set general project variables}
#"..", takes up a level in the directory path
Project <- "FluorO2"

DataInO2 <- file.path("..","ImportData", "Optode")
DataInFRRf <- file.path("..","ImportData", "FRRf")
DataOut <- file.path("..", "FitData")
#CatalogPath <- file.path("../MURIS/MURIS_catalog.csv")
CatalogURL <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"

Run <- "SySlBiolSteps"
# Run <- "MiSaProchloro"

```

```{r set constants}
photons_umol = 6.022E17
A2_m2 = 1E20
us_s = 1000000
```


```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
#library(knitr)
#library(zoo)
library(googlesheets4)
library(googledrive)
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

Import MetaData catalog from MURIS
Improve this if we generalize the approach.
```{r}
# MetaData <- read_csv("../../MURIS_catalog.csv") #two levels from R-folder
```


This chunk reads in a MetaData catalog from googlesheets
Optode Data already merged with MetaData but workflow might need a re-merger.
```{r load Catalog, now as a google sheet}
gs4_deauth()

MetaData <- read_sheet(CatalogURL) %>%
   drop_na(WL) %>%
   mutate(WL = unlist(WL))
 
 as.data.frame(MetaData)

MetaData <- MetaData %>%
  select(-c("Motivation", "Plate", "Well", "InocpH", "FinalpH", "Par_ueAdjusted", "DateOfAdjustment", "ElaspedHoursAtAdjustment" , "ExpEndDate")) %>%
  rename(Calc_umolphotonsm2s1 = `Calculated_µmolPhotons_m-2d-1`)

# sheet is read in by sheet ID, obtained from the URL of the sheet.
# read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
# ggplot/dplyr doesn't like working with a dataframe of lists.
 # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# # # To fix this, first drop all rows missing WL, then unlist.
# # # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.

```


```{r read FRRf data across all runs}
#Temporary RunDate during auditing
#Run <- "SySlCCACaloxy"
FRRfData <- readRDS(file = file.path(DataInFRRf, paste("FluorO2_", Run, "_SolFitsTrim.Rds", sep = "")))

head(FRRfData)
```

# Set Run Specific Variables for each set of O2 Data; TC/noTC, RunDateOxy, StrainID

```{r set run specific O2 variables}
  #FRRf refit includes data from both dates
#RunDateOxy <- 20211210
  #20211213 alternate date
Cuvette <- "TC"
#StrainID <- "MaBe3729"

```

#Filter FRRf data to match selected O2 data
```{r filter FRRfData}
FRRfDataLight <- FRRfData %>%
  filter(!is.na(LR_s)) %>%
  filter(TempCont == Cuvette) %>%
  #filter(CultureID == StrainID) %>%
  filter(Dark1s == 0)


```

Read in Run Specific O2Data
Make this more general as we accumulate more files.
```{r read data}
#temporary hack to cope with run date; replace with GREP? or map?
O2Data <- readRDS(file = file.path(DataInO2, paste("FluorO2_", Run, "_O2Data.Rds", sep = ""))) %>%
  mutate(TempCont = Cuvette)  #add TempCont column for compatibility


head(O2Data)
```


Remove missing rows, reconcile time formats
```{r remove missing rows}
O2Data <- O2Data %>%
  filter(!is.na(LR_s)) %>%
  filter(TempCont == Cuvette) %>%
  filter(LR_s <= 1600) %>% 
  mutate(LR_s = as.numeric(round(LR_s, digits = 0)))


#%>%
  #filter(CultureID == StrainID) %>%
  #mutate(ObsDate = ymd(RunDate),
   #      ObsTime = as.period(AbsTime),
    #     Ex_WL = as.factor(Ex_WL))

head(O2Data)
```

```{r prelimplot O2}
O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(CultureID), cols = vars(Ex_WL)) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 
```


Draw plot from two dataframes
```{r two dataframe plot}
FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = FvFm)) +
  facet_grid(rows = vars(CultureID), cols = vars(Ex_WL, TempCont))

# +
#   scale_colour_manual(values = Colours_nm)

O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL)) +
  facet_grid(rows = vars(CultureID), cols = vars(Ex_WL, TempCont))
  
  #+
  # scale_colour_manual(values = Colours_nm)

```

## Simple left_join, some times lines up
# Many blank rows after left join b/c most O2 rows do not have explicit FRRf row.  Possible problem if ObsTime gets out of sync b/t Optode & FRRf data captures

This problem arises with SySl data; no alignment b/t O2Data & FRRfDataLight based upon ObsTime

Solve using LR_s

Notes 5 Oct 2022
LR_s appears to be calculated incorrectly; jumps from 0 to 550 s

FRRf uses SubProject, O2 uses Run

Include Project & Run in merge

ObsTimeO2 seems incorrect; all NA

Problem with ActPAR after join for
Ex_WL = 445 & SySl1158, SySl1159, SySl1191, SySl1192 (0 only) (ok in SolisenseImportSySl.Rmd)
 SySl1191 (0 only) (ok in SolisenseImportSySl.Rmd)
 Ex_WL = 505 & SySl1189 (missing all data in SolisenseImportSySl.Rmd)
 
 
```{r leftjoin}
colnames(O2Data)

colnames(FRRfDataLight)

intersect(colnames(O2Data),colnames(FRRfDataLight))

#hack fix for 2 bad rows
#   Detected an unexpected many-to-many relationship between `x` and `y`.
# ℹ Row 36014 of `x` matches multiple rows in `y`.
# ℹ Row 201 of `y` matches multiple rows in `x`.
# ℹ If a many-to-many relationship is expected, set `relationship =
#   "many-to-many"` to silence this warning.

O2Data <- subset(O2Data, row.names(O2Data) != 36014)
FRRfDataLight <- subset(FRRfDataLight, row.names(FRRfDataLight) != 201)

O2SlopeData <- left_join(x = O2Data, y = FRRfDataLight, by = c("ObsDate", "CultureID" , "Ex_WL", "LR_s"), suffix = c("O2", "FRRf"), keep = FALSE)

#, 
# "FileDateTime" = "StartDateTimeSol" lines up data when replicates are preformed on same day, "ObsDate" does not have time.

head(O2SlopeData)
```

```{r clean up columns}
colnames(O2SlopeData)

O2SlopeData <- O2SlopeData %>%
  select(-c("LEDSel", "Tau1PQ","Alp2PQ","Tau2PQ","Alp3PQ", "TPQ_PSI", "nm445", "nm470","nm505","nm535","nm590","IR"))
```


 
```{r O2FRRfprelimplot}
O2SlopeData %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_s, y = ActPARCorr), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) +
    theme(strip.text.y = element_text(size = 4, angle=0))

```

```{r remove missing data combinations}
O2SlopeDataClean <- O2SlopeData %>%
  #filter(LR_s <= 800) %>%
  filter(!(Ex_WL == 445 & CultureID %in% c("SySl1247")),
         #!(Ex_WL == 470 & CultureID %in% c("SySl1187")),
         !(Ex_WL == 590 & CultureID %in% c("SySl1227")))

O2SlopeDataClean %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_s, y = ActPARCorr), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  #scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  #scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) +
    theme(strip.text.y = element_text(size = 5, angle=0))
```

Interpolate ActPARCorr estimates across entire time axis.
Problem if LR_s used for join? lose separate LR_sFRRf previously used for interpolations.

Issues with interpolation of ActPAR across Ex_WL and/or ObsDate and/or other boundaries
```{r interpolate FRRf estimates}
#http://publish.illinois.edu/spencer-guerrero/2014/12/11/2-dealing-with-missing-data-in-r-omit-approx-or-spline-part-1/
#https://dplyr.tidyverse.org/dev/articles/colwise.html
#Interpolation causes problems with final rows that repeat last value.

interpolate <- function(x){zoo::na.locf(x, na.rm = FALSE, fromLast = FALSE, type = "l", maxgap = Inf)}

O2SlopeDataClean <- O2SlopeDataClean %>%
  mutate(ActPARCorrinter = interpolate(ActPARCorr)) |>
  ungroup()
 
```

Check whether ActPARCorrinter worked properly
New Problem with Interpolate generating series of 0 values for ActPARCorrinter
Need to fix; has arisen since last run
Groups that have excess 0 ActPARInter are runs with 2 ObsDates of the same CultureID.
Including a 'group_by' does not fix problem.

Problem fixed by rounding LR_s to 0 digits, allows full join of 'FRRfDataLight' with 'O2Data'.

```{r O2FRRfprelimplot2, warning = false}
O2SlopeDataClean %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_s, y = ActPARCorrinter), colour = "black", size = 0.1) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) +
    theme(strip.text.y = element_text(size = 5, angle=0))
  
```

Estimate O2 slopes over LR PAR step ranges
Be careful with nesting!  Multiple steps at single ActPARCorrinter
Filter out first `r induction_s` s of each ActPARCorrinter set to skip 'induction' phase.
Stop fitting at `r_end_s`
26 June 2024 found issue with nesting and slope estimates;
Final ActPARCorrInter == 0 is lost from slope fitting b/c it is lumped in with initial ActPARCorrInter in nest

```{r O2slopes}
induction_s = 60 #hack solution to only take slope of O2 well within given light level
end_s = 170

#TempCont missing?
O2Slopes <- O2SlopeDataClean %>%
  filter(!is.na(ActPARCorrinter)) %>%
  nest(.by =  any_of(c("ObsDate", "FilenameO2", "Project", "CultureID", "Ex_WL", "TempCont", "ActPARCorrinter")))

#head(O2Slopes)

O2Slopes <- O2Slopes %>%
  mutate(O2lm = map(data,  possibly(~ lm(O2_umolL[induction_s:end_s] ~ as.numeric(LR_s[induction_s:end_s]), data = .x), otherwise = NULL)))

# O2Slopes3 <- O2Slopes %>%
#   mutate(O2lm = map(data,  possibly(~ lm(O2_umolL ~ as.numeric(LR_s), data = .x), otherwise = NULL)))

O2Slopes <- O2Slopes %>%
  mutate(O2lm_tidy = map(O2lm, possibly(tidy, otherwise = NULL))) %>%
  #select(-c(O2data, O2lm)) %>%
  unnest(cols = O2lm_tidy) %>%
  filter(term  != "(Intercept)") %>%
  select(-term) %>%
  rename(O2_umolLs = estimate) %>%
  select(-c(statistic, p.value)) %>%
  group_by(ObsDate, FilenameO2, CultureID, Ex_WL) %>% 
  mutate(O2evln_O2ls = ((O2_umolLs - first(O2_umolLs)) * photons_umol)) %>%
  mutate(O2evln_O2lsMIN = ((O2_umolLs - min(O2_umolLs)) * photons_umol)) %>%
  ungroup()

#Decide how to handle subtraction of dark O2 slopes to estimate gross O2 evln
#mutate(O2evln_O2ls_ALT = (O2_umolLs - mean(O2_umolLs[1], O2_umolLs[5]))) %>%
 #- (mean(O2_umolLs[1],O2_umolLs[5])))*6.022e17


```

```{r O2slopeplots}

O2Slopes %>%
  ggplot() +
  geom_point(aes(x = ActPARCorrinter, y = O2_umolLs, colour = Ex_WL)) +
    scale_colour_manual(values = Colours_nm) +
 facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 

O2Slopes %>%
  ggplot() +
  geom_point(aes(x = ActPARCorrinter, y = O2evln_O2ls, colour = Ex_WL)) +
  #geom_line(aes(x = ActPARCorrinter, y = O2evln_O2ls_OLD, colour = "black")) +
    scale_colour_manual(values = Colours_nm) +
facet_grid(cols = vars(Ex_WL), rows = vars(CultureID, ObsDate)) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 

```

Filter runs with positive initial dark slope?
```{r remove positive dark slopes}
# # O2SlopesClean <- O2Slopes %>%
# #   group_by(Date, FilenameO2, Run, ObsDate, CultureID, Ex_WL,  TempCont) %>%
# #     filter(any(O2_umolLs[ActPARCorrinter == 0] > 0)) %>%
# #   ungroup()
# 
# O2SlopesClean <- O2Slopes %>%
#   filter(ActPARCorrinter != 0) %>%
#   #filter(!(Ex_WL == 470 & CultureID %in% c("SySl1156"))) %>%
#   filter(O2evln_O2lsMIN > 0)
# 
# # force remove missing data combinations}
# # O2SlopesClean <- O2SlopesClean %>%
# #   filter(!(Ex_WL == 470 & CultureID %in% c("SySl1156")),
# #          !(Ex_WL == 470 & CultureID %in% c("SySl1187")),
# #          !(Ex_WL == 505 & CultureID %in% c("SySl1189","SySl1191")))
# 
# O2SlopesClean %>%
#   ggplot() +
#   geom_line(aes(x = ActPARCorrinter, y = O2evln_O2lsMIN, colour = Ex_WL)) +
#   #geom_line(aes(x = ActPARCorrinter, y = O2evln_O2ls_OLD, colour = "black")) +
#     scale_colour_manual(values = Colours_nm) +
# facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
#   theme(strip.text.y = element_text(size = 5, angle=0)) +
#   scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
#   scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 
```



# Merge O2Slopes Data with FRRf Data and Catalog

```{r}

O2FRRf <- O2Slopes %>%
  unnest(data) %>%
  filter(!is.na(SourceDataFile)) %>%
  select(-c("Light_1",  "Light_2", "Light_3", "Light_4",  "Light_5", "Light_6", "nm445Corr", "nm470Corr", "nm505Corr", "nm535Corr", "nm590Corr", "IRCorr" ))


O2FRRfMeta <- left_join(x = O2FRRf, y = MetaData, by = c("CultureID" = "SampleID")) 

```

Plot O2 evln curves vs. ActParCorr
```{r O2 evln curves}
O2FRRfMeta %>%
  ggplot() + 
  geom_point(aes(x = ActPARCorr, y = O2_umolLs, colour = CultureID)) +
  facet_grid(cols = vars(Ex_WL), rows = vars(Strain)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "Strain", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) +
  theme_bw()

O2FRRfMeta %>%
  ggplot() + 
  geom_point(aes(x = ActPARCorr, y = O2evln_O2ls, colour = CultureID)) +
  facet_grid(cols = vars(Ex_WL), rows = vars(Strain)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "Strain", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) +
  theme_bw()
  
```


# Cross plots of O2 evolution and FRRf electron transport estimators
# Filter for ActPARCorrinter < 400 to limit saturation responses
```{r O2FRRfcrossplots}
O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2lsMIN, y = JVPSII_aLHIIOxbomax, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Strain)) +
  theme_bw()



O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2lsMIN, y = ETRC_TauAv, colour = Ex_WL, shape = Strain)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2lsMIN, y = ETRC_TauAv, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(Strain)) +
  theme_bw()

O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2lsMIN, y = ETRqpOxbo, colour = Ex_WL, shape = Strain)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2lsMIN, y = ETRqpOxbo, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(Strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2lsMIN, y = JVPSII_ETRC_TauAv_FoSigmax_m2psii, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2lsMIN, y = JVPSII_ETRC_TauAv_FoSigmax_m2psii, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(Strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2lsMIN, y = JVPSII_ETRqpOxbo_FoSigmax_m2psii, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2lsMIN, y = JVPSII_ETRqpOxbo_FoSigmax_m2psii, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(Strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2lsMIN, y = JVPSII_ETRC_TauAv_aLHIIOxboSigmax_m2psii, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2lsMIN, y = JVPSII_ETRC_TauAv_aLHIIOxboSigmax_m2psii, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(Strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2lsMIN, y = JVPSII_ETRqpOxbo_aLHIIOxboSigmax_m2psii, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = O2evln_O2lsMIN, y = JVPSII_ETRqpOxbo_aLHIIOxboSigmax_m2psii, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(Strain)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw()

```

For e- PSII-1 s-1 estimators like ETRqpOxbo, a plot vs. O2 evln_O2ls should give a linear regression.
[PSII] = (O2 evln_O2ls * 4)/(e- PSII-1 s-1)

Graphical Test for stability of [PSII] estimates.
```{r PSIIstabilitytestplot}
O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>% # was < 200 
  filter(Ex_WL == 445) |>
  ggplot() +
  geom_point(aes(y  = (O2evln_O2lsMIN * 4)/ETRqpOxbo, x = ActPARCorr, colour = Ex_WL, shape = Strain)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = ActPARCorr, y = (O2evln_O2lsMIN * 4)/ETRqpOxbo, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(Strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()



O2FRRfMeta %>%
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 400) %>% # was < 200 
  ggplot() +
  geom_point(aes(y  = (O2evln_O2lsMIN * 4)/ETRC_TauAv, x = ActPARCorr, colour = Ex_WL, shape = Strain)) +
  scale_colour_manual(values = Colours_nm) +
  geom_smooth(aes(x = ActPARCorr, y =(O2evln_O2lsMIN * 4)/ETRC_TauAv, colour = Ex_WL), method = "lm") +
  #facet_grid(cols = vars(Strain)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_bw()

```
Progress with SySl CCA data using minimum O2 rate rather than rate at 0 light, probably b/c of issues with induction at start of LRC.

Estimates of [PSII] should be stable vs. ActPARCorr because [PSII] does not change appreciably during duration of light response measure.
If estimate of [PSII] change vs. ActPARCorr it indicates departures from assumptions in underlying data or estimators.

With Max data Filter O2-evolution values that are lower under higher light, caused by photoinhibion/alternative O2-pathways?
This may exclude reasonable values if low light values are exaggerated.
All of SySl data then lost; not applicable in this case
```{r InhibitionFilter}
# O2FRRfMeta590 <- O2FRRfMeta %>%
#   filter(Ex_WL == 590) %>%
#   #filter(O2_umolLs < 0.05) %>% # for MaBe3729 20211210, TC
#   filter(O2evln_O2ls > lag(O2evln_O2ls) & ActPARCorr > lag(ActPARCorr)) #%>%
#   #filter(O2evln_O2ls > lead(O2evln_O2ls)) # for MaBe3726 20211210, noTC
# 
# O2FRRfMeta445 <- O2FRRfMeta %>%
#   filter(Ex_WL == 445) %>%
#   #filter(LR_sFRRfinter != 733) %>% #MaBe3727 20211210, TC
#   #filter(LR_sFRRfinter != 732) %>% #for MaBe3726 20211210, noTC
#   filter(O2evln_O2ls > lag(O2evln_O2ls) & ActPARCorr > lag(ActPARCorr))
# 
# O2FRRfMetaFilter <- rbind(O2FRRfMeta445, O2FRRfMeta590)

```


```{r InhibitionFilteredPSIIstabilitytestplot}
# O2FRRfMetaFilter %>%
#   filter(ETRqpOxbo > 0) %>%
#   ggplot() +
#   geom_point(aes(y  = (O2_umolLs * 4)/ETRqpOxbo, x = ActPARCorr, colour = Ex_WL)) +
#   scale_colour_manual(values = Colours_nm) +
#   #facet_grid(cols = vars(Strain)) +
#   scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
#   theme_bw()
# 
# O2FRRfMetaFilter %>%
#   filter(ETRqpOxbo > 0) %>%
#   ggplot() +
#   geom_point(aes(y  = (O2evln_O2ls * 4)/ETRqpOxbo, x = ActPARCorr, colour = Ex_WL)) +
#   scale_colour_manual(values = Colours_nm) +
#   #facet_grid(cols = vars(Strain)) +
#   scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
#   theme_bw()
# 
# O2FRRfMetaFilter %>%
#   filter(ETRC_TauAv > 0) %>%
#   ggplot() +
#   geom_point(aes(y  = (O2evln_O2ls * 4)/ETRC_TauAv, x = ActPARCorr, colour = Ex_WL)) +
#   scale_colour_manual(values = Colours_nm) +
#   #facet_grid(cols = vars(Strain)) +
#   scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
#   theme_bw()

```


# Fit regressions of FRRf estimators of JVPSII vs. O2evln_O2lsMIN multiply by 4X to convert to e_Ls
Some models fail if intercept forced = 0
```{r JVPSII_e regressions}

O2FRRfMetaModels <-  O2FRRfMeta %>%
  mutate(e_Ls = 4 * O2evln_O2lsMIN) |>
  filter(ActPARCorrinter > 0 & ActPARCorrinter < 200) %>%
  nest(data = -c(Ex_WL)) %>%
  mutate(JVPSII_ETRqpOxbo_FoSigmax_m2psii_e = map(data, possibly(~lm(JVPSII_ETRqpOxbo_FoSigmax_m2psii ~ 0 + e_Ls, data = .x), otherwise = NULL)),
  JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_tidied =  map(JVPSII_ETRqpOxbo_FoSigmax_m2psii_e, possibly(tidy, otherwise = NULL)),
  JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_param = map(JVPSII_ETRqpOxbo_FoSigmax_m2psii_e, possibly(glance, otherwise = NULL)),
   JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_predict =  map(JVPSII_ETRqpOxbo_FoSigmax_m2psii_e, possibly(augment, otherwise = NULL))
  )

O2FRRfMetaModels
```

```{r JVPSII_e regressions}

O2FRRfMetaModels %>%
  unnest(JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_predict) %>%
  ggplot() +
  geom_line(aes(x = e_Ls, y = .fitted), colour = "black", linetype = "dashed") +
 #geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
 #geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
  geom_point(aes(x = e_Ls, y = JVPSII_ETRqpOxbo_FoSigmax_m2psii),colour = "darkgreen") +
  geom_point(aes(x = e_Ls, y = .resid), colour = "darkred", size = 0.1) +
  geom_hline(yintercept = 0,linetype = "dashed") +
  facet_grid(cols = vars(Ex_WL)) +
  theme_bw()

O2FRRfMetaModels %>%
  unnest(JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_predict) %>%
  filter(Ex_WL == 445) |>
  ggplot() +
  geom_line(aes(x = e_Ls, y = .fitted), colour = "black", linetype = "dashed") +
 #geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
 #geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
  geom_point(aes(x = e_Ls, y = JVPSII_ETRqpOxbo_FoSigmax_m2psii),colour = "darkgreen") +
  geom_point(aes(x = e_Ls, y = .resid), colour = "darkred", size = 0.1) +
  geom_hline(yintercept = 0,linetype = "dashed") +
  facet_grid(cols = vars(Ex_WL)) +
  theme_bw()

```

```{r model terms}

JVPSII_eLs_ModelTerms <- O2FRRfMetaModels %>%
  select(-c("data", "JVPSII_ETRqpOxbo_FoSigmax_m2psii_e", "JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_param", "JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_predict")) |>
  unnest(c(JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_tidied), names_sep = "_") |>
  select(-contains("_statistic")) %>%
  pivot_longer(cols = contains(c("estimate", "std.error", "p.value")), names_to = "ModelTerms") |>
   separate(col = ModelTerms, into = c("Model", "Outputs"), sep = "_tidied_") |>
  pivot_wider(values_from = "value",  names_from = "Outputs") |>
  pivot_wider(names_from = "JVPSII_ETRqpOxbo_FoSigmax_m2psii_e_tidied_term", values_from = c("estimate", "std.error", "p.value")) |>
  rename(Slope = `estimate_e_Ls`,
         Slope_SE = `std.error_e_Ls`,
         Slope_P = `p.value_e_Ls`)


```


```{r save O2FRRfMeta}
 saveRDS(O2FRRfMeta, file.path(DataOut, paste(Project, Run, Cuvette, "O2FRRfMeta.Rds", sep = "_"), fsep = .Platform$file.sep))

saveRDS(O2FRRfMetaModels, file.path(DataOut, paste(Project, Run, Cuvette, "O2FRRfMetaModels.Rds", sep = "_"), fsep = .Platform$file.sep))

saveRDS(JVPSII_eLs_ModelTerms, file.path(DataOut, paste(Project, Run, Cuvette, "JVPSII_eLs_ModelTerms.Rds", sep = "_"), fsep = .Platform$file.sep))

# to BalticPhotoperiod
# saveRDS(O2FRRfMeta |> filter(CultureID == "SySl1231" & Ex_WL == 535), file.path(DataOut, paste(Project, Run, Cuvette, "O2FRRfMetaFigureData.Rds", sep = "_"), fsep = .Platform$file.sep))

#JVPSII eLs calibration to BalticPhotoperiod
saveRDS(JVPSII_eLs_ModelTerms, file.path("..", "..", "BalticPhotoperiod", "Data", "CleanedData", "JVPSIIO2Calib", "JVPSII_eLs_ModelTerms.Rds", fsep = .Platform$file.sep))

#JVPSII eLs calibration to BalticPhotoperiod
saveRDS(O2FRRfMetaModels, file.path("..", "..", "BalticPhotoperiod", "Data", "CleanedData", "JVPSIIO2Calib", "O2FRRfMetaModels.Rds", fsep = .Platform$file.sep))

#JVPSII eLs calibration to PicoDiel
saveRDS(JVPSII_eLs_ModelTerms, file.path("..", "..", "PicoDiel", "Data", "CleanedData", paste(Run, Cuvette, "JVPSII_eLs_ModelTerms.Rds", sep = "_"), fsep = .Platform$file.sep))

#JVPSII eLs calibration to BalticO2
saveRDS(JVPSII_eLs_ModelTerms, file.path("..", "..", "BalticO2", "Data", "CleanedData", paste(Run, Cuvette, "JVPSII_eLs_ModelTerms.Rds", sep = "_"), fsep = .Platform$file.sep))

```


