---
title: "FRRO2Compare"
author:
- Douglas A. Campbell
- Maximilian Berthold
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
Compare [O2] to FRRf data for a dataset.

Define time windows defined by changes in PAR imposed by script from FRRf changes in PAR.
For each run create a series of nests of [O2] data from optode for each PAR level and each TempCont setting.
Trim [O2] data nests to remove first 35 rows (~ 35 s) of 180 rows (~ 180 s) to avoid initial induction period.
Fit slopes of umol O2  l~-1~ s~-1~ for each PAR level nest.
Generate estimates of gross umol O2  l~-1~ s~-1~ by subtracting dark respiration rates.
  Initial and final O2 respiration rate estimators; average? chose?
  
  
## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```


```{r set general project variables}
#"..", takes up a level in the directory path
Project <- "FluorO2"

DataInO2 <- file.path("..","ImportData", "Optode")
DataInFRRf <- file.path("..","ImportData", "FRRf")
DataOut <- file.path("..", "FitData")

#For MURIS project data; local copy take from "..Dropbox/MURIS/MURIS_catalog.csv"
CatalogPath <- file.path("../Catalogs/MURIS_catalog.csv")

#For PICO project data
#CatalogURL <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"

Run <- "MaBe"

```


```{r set constants}
photons_umol = 6.022E17
A2_m2 = 1E20
us_s = 1000000
```


```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
#library(knitr)
#library(zoo)
library(googlesheets4)
library(googledrive)
```


```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")

names(Colours_nm) <- Wavelengths_nm
Colours_nm
```


This chunk reads in a MetaData catalog from googlesheets
Optode Data already merged with MetaData but workflow needs a re-merger.
```{r load Catalog, now as a google sheet}
# gs4_deauth()
# 
# MetaData <- read_sheet(CatalogURL) %>%
#    drop_na(WL) %>%
#    mutate(WL = unlist(WL))
#  
#  as.data.frame(MetaData)

```

This chunk reads in a locally stored catalog from .csv.
Optode Data already merged with MetaData but workflow needs a re-merger.
```{r load Catalog, local .csv}
MetaData <- read_csv(CatalogPath)
```


```{r read FRRf data across all runs}
#Run <- "SySlCCACaloxy"
#Run <- "MaBe"
FRRfData <- readRDS(file = file.path(DataInFRRf, paste("FluorO2_", Run, "_SolFitsTrim.Rds", sep = "")))

head(FRRfData)
```


# Set Run Specific Variables for each set of O2 Data; TC/noTC, RunDateOxy, StrainID

```{r set run specific O2 variables}
  #FRRf refit includes data from both dates
#RunDateOxy <- 20211210
  #20211213 alternate date
#StrainID <- "MaBe3729"
#TempCont <- "noTC"


```


#Filter FRRf data to match selected O2 data
```{r filter FRRfData}
FRRfDataLight <- FRRfData %>%
  filter(!is.na(LR_s)) %>%
  filter(Dark1s == 0)

```

Read in Run Specific O2Data
Make this more general as we accumulate more files.
```{r read data}
O2Data <- readRDS(file = file.path(DataInO2, paste("FluorO2_", Run, "_O2Data.Rds", sep = "")))

colnames(O2Data)
```


Remove missing rows, reconcile time formats
```{r remove missing rows}
O2Data <- O2Data %>%
  filter(!is.na(LR_s))

#%>%
  #filter(CultureID == StrainID) %>%
  #mutate(ObsDate = ymd(RunDate),
   #      ObsTime = as.period(AbsTime),
    #     Ex_WL = as.factor(Ex_WL))

colnames(O2Data)

```

```{r prelimplot O2}
O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(CultureID, ObsDate), cols = vars(Ex_WL, TempCont)) +
  xlim(0, 1000) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) +
  coord_cartesian(xlim = c(0, 1200))

```

Draw plot from two dataframes
```{r two dataframe plot}
FRRfDataLight %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = FvFm)) +
  facet_grid(rows = vars(CultureID, ObsDate), cols = vars(Ex_WL, TempCont)) +
  scale_colour_manual(values = Colours_nm)

O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL)) +
  facet_grid(rows = vars(CultureID, ObsDate), cols = vars(Ex_WL, TempCont)) +
  scale_colour_manual(values = Colours_nm)

```


```{r leftjoin}
colnames(O2Data)
colnames(FRRfDataLight)

FRRfDataLight <- FRRfDataLight %>% 
  mutate(Date = ymd(ObsDate))

#LR_s

#removed some columns missing from O2Data
O2SlopeData <- left_join(x = O2Data, y = FRRfDataLight, by = c("Date", "CultureID", "Ex_WL", "TempCont", "LR_s"), suffix = c("O2", "FRRf"), keep = FALSE) %>%
  select(-c("Dark1s", "nm470":"IRCorr"))

#O2SlopeData <- left_join(x = O2Data, y = FRRfData, by = c(c("Date" = "ObsDate"), c("AbsTime" = "ObsTime"), "CultureID", "Ex_WL"), suffix = c("O2", "FRRf"), keep = FALSE) %>%
#  select(c("Date":"Act_PAR", "ActPAR_photonsm2s"))

colnames(O2SlopeData)
```
Fixed:
O2 curves from 2021-12-13 have no matching FRRf data in O2SlopeData even though FRRfDataLight$Date has both "2021-12-10" "2021-12-13"!

O2 and FRRf runs with/without TC
Issue with LR_s estimate for 2021-12-13

join by LR_s misses some FRRf data; issue with calculation?

1/2 of LR_s estimates off by ~2400 s fixed by including TempCont in grouping for LR_s estimates
```{r O2FRRfprelimplot}
O2SlopeData %>%
  #filter(Date == "2021-12-13" ) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL)) +
  geom_point(aes(x = LR_s, y = ActPARCorr)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL, TempCont), rows = vars(CultureID, Date)) +
  theme_bw()
```

Interpolate ActPAR estimates across entire time axis
```{r interpolate FRRf estimates}
#http://publish.illinois.edu/spencer-guerrero/2014/12/11/2-dealing-with-missing-data-in-r-omit-approx-or-spline-part-1/
#Interpolation causes problems with final rows that repeat last value.

O2SlopeData <- O2SlopeData |>
  filter(LR_s < 1000)

#type = "l",

interpolate <- function(x){zoo::na.locf(x, na.rm = FALSE, fromLast = FALSE,  maxgap = Inf)}

O2SlopeData <- O2SlopeData %>%
  mutate(ActPARinter = interpolate(ActPAR),
         LR_sinter = interpolate(LR_s), .after = Temp_C)
         
```

Check whether ActPARinter worked properly

Issues with:
All runs start with ActPARinter > 0, or 0 for only a very short time.
possible that ActPARinter is displaced leftwards to lower LR_s values than appropriate
  Fixed by setting 'fromLast = FALSE' in zoo::na.locf and removing unused 'type = "l" argument

MaBe3729, noTC, 445, 2021-12-13  ActPARinter = 0 throughout
MaBe3729, noTC, 590, 2021-12-13  ActPARinter only goes to 90

OK otherwise

```{r O2FRRfprelimplot2}
#filter CultureID with negative O2slope throughout and with aberrant ActPARinter
#recheck with Max about FRRf file processing to recuperate ActPARinter
O2SlopeDataFilter %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  geom_point(aes(x = LR_s, y = ActPARinter), colour = "black") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL, Date), cols = vars(CultureID, TempCont)) +
  theme_bw()

```

Estimate O2 slopes over LR PAR step ranges
Be careful with nesting!  Multiple steps at single ActPARinter
Filter out first 35 s of each ActPARinter set to skip 'induction' phase.
Filter out last 5 s to avoid Dark1s = 1 rows
```{r O2slopes}
induction_s = 35
end_s = 175

#For now filter out issues with ActPARinter
O2SlopeDataFilter <- O2SlopeData %>%
  filter(!(CultureID == "MaBe3729" & TempCont == "noTC" & Date == "2021-12-13"))

O2Slopes <- O2SlopeDataFilter %>%
  nest(O2data = -c(ProjectO2, Date, CultureID, FilenameO2,  Al_WL, Ex_WL, TempCont, ActPARinter, )) %>% 
  mutate(O2lm = map(O2data,  possibly(~ lm(O2_umolL[induction_s:end_s] ~ as.numeric(LR_s[induction_s:end_s]), data = .x), otherwise = NULL)),
         O2lm_tidy = map(O2lm, possibly(tidy, otherwise = NULL))) %>%
  select(-c(O2data, O2lm)) %>%
  unnest(cols = O2lm_tidy) %>%
  filter(term  != "(Intercept)") %>%
  select(-term) %>%
  rename(O2_umolLs = estimate) %>%
  group_by(Date, FilenameO2, CultureID, Ex_WL) %>% #careful with group_by; this only works with a single replication of each LR
  mutate(O2evln_O2ls = (O2_umolLs - min(O2_umolLs)) * 6.022e17) %>%
  ungroup()

#Decide how to handle subtraction of dark O2 slopes to estimate gross O2 evln
#mutate(O2evln_O2ls_ALT = (O2_umolLs - mean(O2_umolLs[1], O2_umolLs[5]))) %>%
 #- (mean(O2_umolLs[1],O2_umolLs[5])))*6.022e17
```


```{r O2slopeplots}

O2Slopes %>%
  ggplot() +
  geom_line(aes(x = ActPARinter, y = O2_umolLs, colour = Ex_WL)) +
    scale_colour_manual(values = Colours_nm) +
    facet_grid(cols = vars(CultureID, Date), rows = vars(Ex_WL, TempCont)) +
    theme_bw()

O2Slopes %>%
  ggplot() +
  geom_line(aes(x = ActPARinter, y = O2evln_O2ls, colour = Ex_WL)) +
    scale_colour_manual(values = Colours_nm) +
    facet_grid(cols = vars(CultureID, Date), rows = vars(Ex_WL, TempCont)) +
    theme_bw()
```

Merge O2Slopes Data with FRRf Data and Catalog
It should be possible to do this with more clever unnesting.
```{r}
O2FRRfMeta <- left_join(x = FRRfDataLight, y = O2Slopes, by = c("Date",  "CultureID", "Ex_WL", "TempCont", "ActPAR" = "ActPARinter"), suffix = c("FRRf", "O2"), keep = FALSE) %>%
  left_join(x = ., y = MetaData, by = c("CultureID" = "id"))

#filter out cols that are all NA
#https://stackoverflow.com/questions/2643939/remove-columns-from-dataframe-where-all-values-are-na

O2FRRfMeta <- O2FRRfMeta %>% 
  select(where(~!all(is.na(.x))))

colnames(O2FRRfMeta)
```

Cross plots of O2 evolution and FRRf electron transport
```{r O2FRRfcrossplots}
O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIOxbomax > 0) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls, x = JVPSII_aLHIIOxbomax, colour = Ex_WL)) +
  geom_smooth(aes(y = O2evln_O2ls, x = JVPSII_aLHIIOxbomax, colour = Ex_WL), method = "lm") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(TempCont), rows = vars(strain)) +
  theme_bw()

O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_ETRtauav_FoSig > 0) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls, x = JVPSII_ETRtauav_FoSig, colour = Ex_WL)) +
  geom_smooth(aes(y = O2evln_O2ls, x = JVPSII_ETRtauav_FoSig, colour = Ex_WL), method = "lm") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(TempCont), rows = vars(strain)) +
  theme_bw()


O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_ETRqpOxbo_FoSig > 0) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls, x = JVPSII_ETRqpOxbo_FoSig, colour = Ex_WL)) +
  geom_smooth(aes(y = O2evln_O2ls, x = JVPSII_ETRqpOxbo_FoSig, colour = Ex_WL), method = "lm") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(TempCont), rows = vars(strain)) +
  theme_bw()

O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_ETRtauav_aLHII_Sig > 0) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls, x = JVPSII_ETRtauav_aLHII_Sig, colour = Ex_WL)) +
  geom_smooth(aes(y = O2evln_O2ls, x = JVPSII_ETRtauav_aLHII_Sig, colour = Ex_WL), method = "lm") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(TempCont), rows = vars(strain)) +
  theme_bw()

O2FRRfMeta %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_ETRqpOxbo_aLHII_Sig > 0) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls, x = JVPSII_ETRqpOxbo_aLHII_Sig, colour = Ex_WL)) +
  geom_smooth(aes(y = O2evln_O2ls, x = JVPSII_ETRqpOxbo_aLHII_Sig, colour = Ex_WL), method = "lm") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(TempCont), rows = vars(strain)) +
  theme_bw()

```


Fit regressions of FRRf estimators vs. O2evln
```{r FRRFO2regressions}
O2FRRfMetaNest <-  O2FRRfMeta %>%
  filter(strain != "PCC6803") %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIOxbomax > 0) %>%
  nest(data = -c(Ex_WL, TempCont)) %>%
  mutate(
  JVPSII_aLHIIOxbomax_O2 = map(data, possibly(~lm(JVPSII_aLHIIOxbomax ~ 0 + O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_aLHIIOxbomax_O2_predict = map(JVPSII_aLHIIOxbomax_O2, possibly(augment, otherwise = NULL)),
  JVPSII_aLHIIOxbomax_O2_tidied =  map(JVPSII_aLHIIOxbomax_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_aLHIIOxbomax_O2_param = map(JVPSII_aLHIIOxbomax_O2, possibly(glance, otherwise = NULL)),
  JVPSII_ETRqpOxbo_FoSig_O2 = map(data, possibly(~lm(JVPSII_ETRqpOxbo_FoSig ~ 0 + O2evln_O2ls, data = .x), otherwise = NULL)),
  JVPSII_ETRqpOxbo_FoSig_O2_predict = map(JVPSII_ETRqpOxbo_FoSig_O2, possibly(augment, otherwise = NULL)),
  JVPSII_ETRqpOxbo_FoSig_O2_tidied =  map(JVPSII_ETRqpOxbo_FoSig_O2, possibly(tidy, otherwise = NULL)),
  JVPSII_ETRqpOxbo_FoSig_O2_param = map(JVPSII_ETRqpOxbo_FoSig_O2, possibly(glance, otherwise = NULL))
  )


O2FRRfMetaNest %>%
  unnest(JVPSII_aLHIIOxbomax_O2_predict) %>%
  ggplot() +
  geom_line(aes(x = O2evln_O2ls, y = .fitted), colour = "black", linetype = "dashed") +
 # geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
 #   geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIOxbomax),colour = "darkgreen") +
  geom_point(aes(x = O2evln_O2ls, y = .resid), colour = "darkred", size = 0.1) +
  geom_hline(yintercept = 0,linetype = "dashed") +
  facet_grid(cols = vars(Ex_WL), rows = vars(TempCont)) +
  theme_bw()

O2FRRfMetaNest %>%
  unnest(JVPSII_aLHIIOxbomax_O2_tidied)

O2FRRfMetaNest %>%
  unnest(JVPSII_ETRqpOxbo_FoSig_O2_predict) %>%
  ggplot() +
  geom_line(aes(x = O2evln_O2ls, y = .fitted), colour = "black", linetype = "dashed") +
 # geom_line(aes(x = O2evln_O2ls, y = .fitted + .se.fit), colour = "grey", linetype = "dashed") +
 #   geom_line(aes(x = O2evln_O2ls, y = .fitted - .se.fit), colour = "grey", linetype = "dashed") +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_ETRqpOxbo_FoSig),colour = "darkgreen") +
  geom_point(aes(x = O2evln_O2ls, y = .resid), colour = "darkred", size = 0.1) +
  geom_hline(yintercept = 0,linetype = "dashed") +
  facet_grid(cols = vars(Ex_WL), rows = vars(TempCont)) +
  theme_bw()

O2FRRfMetaNest %>%
  unnest(JVPSII_ETRqpOxbo_FoSig_O2_tidied)

```


```{r save O2FRRfMeta}
saveRDS(O2FRRfMeta, file.path(DataOut, paste(Project, RunDate, "O2FRRfMeta.Rds", sep = "_"), fsep = .Platform$file.sep))
```
